refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-07-24 paper/manuscript.tex
Make abstract single paragraph as required
Trim down abstract to manageable length

\begin{abstract}
The \refnx\ package is designed for object-oriented model-based analysis of neutron and X-ray reflectometry data in Python. It is cross platform, and has been tested on Linux, macOS, and Windows.

Structure construction is modular, being composed from a series of Components that each describe a subset of the interface. These Components (such as LipidLeaflet, or Spline) allow the user to parameterise their model in terms of physically relevant parameters. The Model and data are used to create an Objective, which is used to calculate residuals, log-likelihood, and log-prior probabilities of the system. Objectives are combined to perform co-refinement of multiple datasets, and mixed-area models. All parameters in the system can have a variety of Bounds applied; these Bounds consist of probability distributions which represent their prior probability. The prior probability encodes a user's knowledge about the Parameter values, which allows the curve-fitting engine to direct solutions toward a more probable parameter space. Extra prior probability terms can be defined for Components, over and above those available from the Parameters alone. Algebraic Parameter constraints are available.

The powerful curve-fitting engine offers the choice of using a normal least-squares fitting approach (with a variety of global and gradient-based optimizers) or a Bayesian approach using Markov Chain Monte Carlo to investigate the posterior distribution of the model parameters. The Bayesian approach is useful in examining parameter covariances, model selection, and variability in the resulting scattering length density profiles. Whilst the main intention of the program is to analyse reflectometry data it is equally adept for generalised curve-fitting purposes.

The whole package is designed with a focus on reproducible research; its use in \Jupyter\ notebooks (which includes a graphical user interface), and subsequent distribution of those notebooks as supporting information, permits scientists to straightforwardly reproduce analyses made by others.
\end{abstract}

>>>>

\begin{abstract}
The \refnx\ package is designed for object-oriented model-based analysis of neutron and X-ray reflectometry data in Python. It is cross platform, and has been tested on Linux, macOS, and Windows.
Model construction is modular, being composed from a series of components that each describe a subset of the interface, parameterised in terms of physically relevant parameters (volume fraction of a polymer, lipid area per molecule, etc). The model and data are used to create an objective, which is used to calculate residuals, log-likelihood, and log-prior probabilities of the system. Objectives are combined to perform co-refinement of multiple datasets, and mixed-area models. Prior knowledge of parameter values is encoded as probability distribution functions or bounds on all parameters in the system. Extra prior probability terms can be defined for Components, over and above those available from the Parameters alone. Algebraic Parameter constraints are available.
A choice of fitting approaches is available include least-squares (global and gradient-based optimizers) and a Bayesian approach using Markov Chain Monte Carlo to investigate the posterior distribution of the model parameters. The Bayesian approach is useful in examining parameter covariances, model selection, and variability in the resulting scattering length density profiles.
The package is designed to facilitate reproducible research; its use in \Jupyter\ notebooks (which includes a graphical user interface), and subsequent distribution of those notebooks as supporting information, permits straightforward reproduction of analyses.
\end{abstract}
